Work Fragmentation in Developer Interaction Data

### 2016-02-09 paper_2.tex
Lineplot in RQ2

The Table \ref{tbl:udc_stats_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity.

The difference between categories seems to decrease when reaching higher values. There is a clear difference between the low and medium categories of proportions, but the difference between medium and high is minor. The same happens when comparing the categories [1-3] and [4-6] of the number of interruptions, and the categories [4-6] and $>$6. In other words, as the value of the metrics get higher, the negative effect (according to these metrics) changes at a very low rhythm.

>>>>

The Table \ref{tbl:udc_stats_dur_int} and shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity.

The difference between categories seems to decrease when reaching higher values. There is a clear difference between the low and medium categories of proportions, but the difference between medium and high is minor. The same happens when comparing the categories [1-3] and [4-6] of the number of interruptions, and the categories [4-6] and $>$6. In other words, as the value of the metrics get higher, the negative effect (according to these metrics) changes at a very low rhythm. The Figure \ref{fig:udc_lines_dur_int} shows the same results in the form of line plots where is more easy to verify via visual inspection. In this Figure the color of the lines represent the classification for the proportion of prolonged interruptions.

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\minipage{1\textwidth}
		\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_lines_dur_int}  \\
		\endminipage\hfill
	\end{tabular}
	\caption{Plot showing the median values for the metrics according to the proportion of prolonged interruptions and the number of interruptions in UDC . }
	\label{fig:udc_lines_dur_int}
\end{figure}
